---
title: "formative.rmd"
author: "Yang XU"
date: "October 5, 2017"
output: html_document
---

```{}
D1 <- read.csv("~/Downloads/HMXPC13_DI_v2_5-14-14.csv")
```


Q6:How many people enrolled in HarvardX/CS50x recieved certification in 2012? (Please inlcude your code in your markdown document)?
A: There are in total 1287 students enrolled in HarvardX/CS50x recieved certification in 2012.
```{r}
sum(D1$course_id == "HarvardX/CS50x/2012" & D1$certified == "1")
```

Q7: How many people registered for HarvardX/CS50x from Columbia on October 15, 2012? (Please inlcude your code in your markdown document)
A:There are 10 people registered for the course from Columbia on October 15,2012, BUT! there 0 people registered from Columbia that day, if this is teh answer you oringinally asked for.
```{r}
sum(D1$course_id == "HarvardX/CS50x/2012" & D1$final_cc_cname_DI == "Colombia" & D1$start_time_DI == "2012-10-15")
```


Q8:Create a new data frame (D2) that includes student ID and registration date for all students from a country of your choice (Please inlcude your code in your markdown document)
```{r}
D2 <- subset(D1, final_cc_cname_DI == "Australia",select = c(userid_DI,start_time_DI,final_cc_cname_DI))
D2
```

Q9:Create a new data frame (D3) in which the column names are the registration dates, with one column containing the student ids and all other cells indicating a 1 if the student registered on that date or an NA if they did not (hint: you will need to create a new variable before you change the structure of your data frame)
```{r}
library(tidyr)
library(dplyr)
D3 <- D2[c("userid_DI","start_time_DI")]
D3$default_value <-1
D3 <- mutate(D3, row=row_number())
D3
D3 <- tidyr::spread(D3, key="start_time_DI",value="default_value", fill = NA, convert = FALSE, drop = TRUE)
D3
```

Q10:Now make the row names of D3 the student ids on your new data frame and remove the user id column from your data frame
(so it is changing the variable row to student_id)
```{r}
names(D3)[names(D3) == 'row'] <- 'student_id'
D3
#now to drop the user_id, which is the first column 
D3 <- subset(D3, select = -1)
D3
```
Q11:Convert your data frame to a matrix (M1)
```{r}
M1 <-as.matrix(D3)
M1
```

Q12:Create a new matrix which is the transposed version of your matrix (M2)
```{r}
M2 <-t(M1)
M2
```

Q13:Create a third matrix (M3) that is a student by student matrix where the cells in the matrix represent if two studentes registered on the same day (This will take a lot of processing power, you may not be able to complete it if you have a large number of students)

```{r}
#to creat a student by student matrix, so just do matrix multiplication
M3<-M1 %*% M2
```

Q14:Convert the diagonal of your matrix into NAs
```{r}
diag(M3) <- NA
```
